\documentclass{cv_TOH}

\usepackage[letterpaper,top=2cm,bottom=2cm,left=2cm,right=2cm]{geometry}
\usepackage{hyperref}

\pagenumbering{gobble}

\begin{document}

\name{Timothy O. Hodson}
\shortcontact{tohodson@gmail.com}{(217) 493-5551}
\vspace{-0.2cm}
\centerline{\footnotesize{[digital version of this document embeds links]}}

\section{Education}
\datedsubsection{\textbf{Ph.D. student in Geology} \textit{-- Northern Illinois University}}{In progress}
\datedsubsection{\href{http://www.niu.edu/geog/giscert/graduate_certificate.shtml}{Certificate of Graduate Study in Geographic Information Analysis}}{2014}
\datedsubsection{\href{http://gradworks.umi.com/15/28/1528822.html}{\textbf{M.S. Geology} \textit{-- Northern Illinois University}}}{2012}
\datedsubsection{\textbf{B.S. Geology and Geophysics} \textit{-- University of Wisconsin, Madison}}{2007}

\section{Research Interests}
\begin{itemize}
\item Reconstructing glacier and ice sheet dynamics from the sedimentary record.
\item Application of remote sensing and geophysical data to surficial and seafloor mapping. 
\end{itemize}

\section{Professional Experience}

\datedsubsection{Research Assistant, \textit{Northern Illinois University}}{2010--Present}
\begin{itemize}
\item \href{http://www.wissard.org}{Researcher and sensor technician for WISSARD, a NSF funded project to explore environments beneath the Antarctic Ice Sheet. }\href{http://discovermagazine.com/2014/jan-feb/12-the-search-for-life-trapped-under-ice}{Listed \#12 in \textit{Discover}'s Top 100 Science Stories of 2013}
\item Mapped seafloor habitats of Puget Sound, Washington by fusing historical and modern datasets. Resulting maps will inform public and policy makers in developing better conservation and management of Puget Sound.
\item \href{http://pubs.usgs.gov/sim/3253/}{Mapped seafloor habitats in Glacier Bay National Park using remotely sensed data and seafloor video transects in a maximum likelihood classifier. Resulting report and mapset published by USGS.}
\end{itemize}

\datedsubsection{Teaching Assistant, \textit{Northern Illinois University}}{2010--2011}
\begin{itemize}
\item Teaching assistant for courses in sedimentology, paleontology, and planetary science.
\end{itemize}

\datedsubsection{Research Assistant, \textit{Illinois State Geological Survey}}{2008--2009}
\begin{itemize}
\item \href{http://www.isgs.illinois.edu/sites/isgs/files/maps/isgs-quads/aurora-south-sg.pdf}{Created geologic maps from LIDAR, geologic drill cores and satellite imagery.}
\item Conducted fieldwork around Illinois including geophysical surveying, geologic drilling, and well installation for watershed and aquifer characterization. 
\end{itemize}

\section{Other Experience}
\begin{itemize}
\item\href{http://www.niutoday.info/2014/04/17/niu-student-lands-coveted-internship-aboard-exploration-ship/}{Mapping intern aboard NOAA's E/V Okeanos Explorer. Duties included QA and processing of data collected by the ship's swath and subbottom sonars.}
\item STEMfest volunteer communicating importance of polar reasearch and organizing educational outreach activities for k-12 students.
\end{itemize}

\section{Programming}
\begin{itemize}
\item Python, C, Matlab, R, BASH, JavaScript, SQL, HTML/CSS
\item Relevant coursework in geospatial methods and modeling, web mapping, and network applications in C.
\item Familiar with common libraries for numerical programming, data viz, geospatial analysis, and stats.
\item \href{https://github.com/tohodson/velodyne_tools}{Wrote a LIDAR instrument driver in C as an independent study.}
\end{itemize}

\section{Software}
ArcGIS (4yrs), Adobe Illustrator, QGIS, GRASS, Fledermaus, Microsoft Office, Unix utilities, Emacs, and Vim

\section{Professional organizaitons}
American Geophysical Union, Sigma Xi (Associate Member), Geological Society of America

\section{References}
\begin{tabular}{@{}p{6cm}p{6cm}p{6cm}}
 \textbf{Thomas Pingel}            & \textbf{John Winans}              &   \textbf{Ross Powell}           \\
 Asst. Professor                   &  Research Associate               &   Professor (Advisor)            \\ 
 Geography                         &  Computer Science                 &   Geology and Env. Geoscience    \\
 Northern Illinois University      &  Northern Illinois University     &   Northern Illinois University   \\ 
 DeKalb, Illinois                  &  DeKalb, Illinois                 &   DeKalb, Illinois               \\
 phone: (815) 753-9208             &  phone: (815) 753-5947            &   phone: (815) 753-7952          \\
 e-mail: tpingel@niu.edu           &  e-mail: jwinans@niu.edu          &   e-mail: rpowell@niu.edu        \\
 \url{www.tpingel.com}             &  \url{faculty.cs.niu.edu/~winans} &                                  \\     
\end{tabular}

\end{document} 
