%__________________________________________________________________________________________________________________
% Professional Experience
\section{Professional Experience}

\datedsubsection{\textbf{Academic Hourly}, \textit{Illinois State Water Survey}}{2015--Present}
\begin{itemize}
\item Field coordinator for NSF funded Critical Zone Observatory investigating the sustainability of intensively managed landscapes. 
  Duties include maintaining stream gaging stations, data aquisition and processing. 
\end{itemize}

\datedsubsection{\textbf{Webmapping Intern}, \textit{Historic Preservation Commission, City of Urbana}}{Fall, 2015}
\begin{itemize}
\item Built an interactive webmap of historical buildings in the city of Urbana. 

\end{itemize}

\datedsubsection{\textbf{Research Assistant}, \textit{Northern Illinois University}}{2010--2015}
\begin{itemize}
\item \href{http://www.wissard.org}{Researcher and technician for WISSARD, an
  integrative study to explore aquatic environments beneath the Antarctic Ice
  Sheet.}
  \href{http://discovermagazine.com/2014/jan-feb/12-the-search-for-life-trapped-under-ice}
       {Listed \#12 in \textit{Discover}'s Top 100 Science Stories of 2013.} Helped in developing data acquisition software and sensor integration.
       Other duties included maintenance and operation of oceanographic instruments and operational equipment,
       report writing, organizing purchase and shipment of field supplies and equipment.
  
\item Mapped seafloor habitats and geology of Puget Sound as part of The Nature
  Conservancy's initiative to foster public awareness and conservation of marine
  environments. Resulting mapsets in publication with USGS.

\item \href{http://pubs.usgs.gov/sim/3253/}{Mapped seafloor habitats and geology
  of Glacier Bay National Park from swath bathymetry, seafloor video transects, and a supervised classifier. Resulting report and map set published by USGS.}
  
\end{itemize}

\datedsubsection{\textbf{Mapping Intern}, \textit{UCAR}}{August,2014}
\begin{itemize}
\item \href{http://www.niutoday.info/2014/04/17/niu-student-lands-coveted-internship-aboard-exploration-ship/}
  {Sailed as a survey watchstander aboard NOAA's \textit{E/V Okeanos Explorer}.
  Duties included QA and processing of data collected by the ship's swath and sub-bottom sonars.}
\end{itemize}

\datedsubsection{\textbf{Teaching Assistant}, \textit{Northern Illinois University}}{2010--2011}
\begin{itemize}
\item Teaching assistant for courses in sedimentology, paleontology, and planetary science.
\end{itemize}

\datedsubsection{\textbf{Academic Hourly}, \textit{Illinois State Geological Survey}}{2008--2009}
\begin{itemize}
\item \href{http://www.isgs.illinois.edu/sites/isgs/files/maps/isgs-quads/aurora-south-sg.pdf}{Prepared geologic maps from LIDAR data, drill cores and satellite imagery.}
\item Conducted fieldwork around Illinois including geophysical surveying, geologic drilling, and well logging for watershed and aquifer characterization. 
\end{itemize}
